---
title: "lab7"
author: "Caroline Shepherd"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE, include = TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)
```

```{r}
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Explore penguins

Use 'GGally::ggpairs()' to create a pairs plot

```{r}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot.

-species
-bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```
## Multiple linear regression

we are going to try to understand (a bit better) the relationships between multiple predictor variables and an outcome variable, which is penguin body mass.

The different predictor variables we're going to try are things like:
-species
-flipper length
-sex
-bill depth


### Model 1

Model body mass based on only flipper length and bill depth (this is a bad idea - there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Call model by name to return only coefficients
model_1

# If I want to get more information on the model and coefficients
summary(model_1)
```

for 'model_1' (just run code and see the coefficients):
Flipper length - for each 1 mm increase in flipper length we expect (on average) penguin body mass to increase by 51.54 grams if everything else is held constant.

R Squared value means
76% of variants in penguin body mass is explained by flipper length and bill depth in this model
This is less than 100% because something is missing - in this case, sex would probably be an important variable we should include

Actually, we think that a model for penguin body mass should contain the variables species, flipper length, and sex

```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)

# Let's check out the coefficients:
model_2
```

Adelie must be the reference layer because it doesn't show up after 'model_2' - female and adelie have been assigned to 0

# Interpreting the coefficients for:
flipper length - For each 1mm increase in flipper length, we expect to see penguin body mass to incresae by 20.02

Gentoo: If everything else is held constant, I would expect a penguin from that population to weigh 836.26 grams larger than an Adelie if everything else about them is the same

Male: If everything else is held constant, I would expect a male penguin to be 530.38 grams larger than a female penguin if everything else about them is the same


## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)

```

## A couple ways to get and report MLR model outcomes

use broom::tidy() to get model coefficient ifo into a tidy dataframe

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```

Try to write inline code that spits out the coefficient for gentoo here

`r penguin_model2_coef$estimate[4]`


## Look at the model diagnostics

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table

use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer

```{r, results = "asis"}
stargazer(model_2, type = "html")
```

